---
title: "search_str"
output: html_document
date: "2024-06-21"
---

There are 2 main ways to match strings grep from base r and str_ from tidyverse.

we use stringi to generate some random text for demonstration

```{r setup, include=FALSE}

library(stringr)
sample_small <- stringi::stri_rand_lipsum(100)

```

grep provides the position of a pattern in the character vector, just as it's equivalent str_which does:

```{r}
grep("Lorem", sample_small)
```
```{r}
str_which(sample_small, "Lorem")
```
grepl/str_detect on the other hand give you the information for each element of the vector, if it contains the string or not.


```{r}
grepl("Lorem", sample_small)
```

```{r}
str_detect(sample_small, "Lorem")
```

Now in terms of why to use stringr over base, I think there are two arguments: different syntax makes it a little bit easier to use stringr with pipes


```{r}
library(dplyr)
sample_small %>% 
  str_detect("Lorem")
```
compared to:

```{r}
sample_small %>% 
  grepl("Lorem", .) 
```

And stringr is roughly 5x faster than base (for the two functions we are looking at):

```{r}
library(bench)
sample_big <- stringi::stri_rand_lipsum(100000)
bench::mark(
  base = grep("Lorem", sample_big),
  stringr = str_which(sample_big, "Lorem")
)
```

It is important to highlight that they treat N/A different:
```{r}
vector <- c("private Reise", NA, NA)
stringr::str_detect(vector, "privat")
```
```{r}
grepl("privat", vector)
```
with this in mind, let look at str_detect options:
* str_detect() is case-sensitive
* you can use regex (rugular expression):

eg.g str_detect(colnames(df), "^c[54]|c[54]$")
where:
* ^ - start of string
* c - a c
* [45] - 4 or 5
* | - or
* c[45] - c4 or c5 ...
* $ - ... at the end of the string.

```{r}
sample_small %>% 
  str_detect("^Lor|em$")
```
for more material about regex go to : https://stringr.tidyverse.org/articles/regular-expressions.html


